Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-11-19 grove-paper.tex
Try "Share Edits" instead of "Sync" in diagram

%\figureCommutativity
\begin{figure}
  \centering
  \begin{tikzpicture}
    \path (-3cm, 0cm) node (a) [align=center]       {Original \\ Version};
    \path ( 0cm, 1cm) node (b) [align=center,alice node] {Alice's  \\ Version};
    \path ( 0cm,-1cm) node (c) [align=center,bob node]   {Bob's    \\ Version};
    \path ( 3cm, 0cm) node (d) [align=center]       {Synchronized \\ Version};
    \path [draw,->,alice step] (a) -- node [pos=0.7,auto,align=center] {Alice's \\ Edits} (b);
    \path [draw,->,bob step]   (a) -- node [pos=0.7,auto,swap,align=center]      {Bob's \\ Edits}   (c);
    \path [draw,->,merge step] (b) -- node [pos=0.3,auto] {Sync} (d);
    \path [draw,->,merge step] (c) -- node [pos=0.3,auto,swap]      {Sync} (d);
  \end{tikzpicture}
  \caption{Commutativity of Edits.}
  \label{fig:Commutativity}
\end{figure}

>>>>

%\figureCommutativity
\begin{figure}
  \centering
  \begin{tikzpicture}
    \path (-3cm, 0cm) node (a) [align=center]            {Original \\ Version};
    \path ( 0cm, 1cm) node (b) [align=center,alice node] {Alice's  \\ Version};
    \path ( 0cm,-1cm) node (c) [align=center,bob node]   {Bob's    \\ Version};
    \path ( 3cm, 0cm) node (d) [align=center]            {Synchronized \\ Version};
    \path [draw,->,alice step] (a) -- node [pos=0.7,align=center,auto]      {Alice's \\ Edits} (b);
    \path [draw,->,bob step]   (a) -- node [pos=0.7,align=center,auto,swap] {Bob's \\ Edits}   (c);
    \path [draw,->,merge step] (b) -- node [pos=0.3,align=center,auto]      {Share \\ Edits} (d);
    \path [draw,->,merge step] (c) -- node [pos=0.3,align=center,auto,swap] {Share \\ Edits} (d);
  \end{tikzpicture}
  \caption{Commutativity of Edits.}
  \label{fig:Commutativity}
\end{figure}
